\vspace{30mm} {\Large\bf RISC-V Duo-PLIC for the Advancced Interrupt Architecture} \\ {\large Document Version \DuoPLICRev}

### 2023-06-11 doc/src/preface.tex
Add clarification about MSI write replaced by MRIF update
Signed-off-by: Anup Patel <apatel@ventanamicro.com>
Added clarification about the term IOMMU
Signed-off-by: David Kruckemyer <dkruckemyer@ventanamicro.com>
Signed-off-by: Anup Patel <apatel@ventanamicro.com>
Better align indirect registers with hypervisor, Smcsrind extensions
When vsiselect has a reserved value, attempts to access sireg from 
a virtual machine (VS or VU-mode) should preferably raise an illegal
instruction exception instead of a virtual instruction exception.

Note also that attempts to access Smcsrind's additional alias

>>>>

\section*{Changes for RC5 (Ratification Candidate 5)}

Better aligned the rules for indirectly accessed registers with the
hypervisor extension and with forthcoming extension Smcsrind/Sscsrind.
In particular, when \z{vsiselect} has a reserved value, attempts
to access \z{sireg} from a virtual machine (VS or \mbox{VU-mode})
should preferably raise an illegal instruction exception
instead of a virtual instruction exception.

Added clarification about MSI write replaced by MRIF update and
notice MSI sent after the update.
